ECML/PKDD 2016 Discovery Challenge \\ Bank Branch Visits and Customer Acquisition Prediction using Gradient Boosted Trees

### 2016-09-05 paper/paper.tex
updated

@@

%If there are too many authors, use \authorrunning
%\authorrunning{First Author et al.}
\institute{
    Data Scientist, Asia Miles Limited
    \\ \authormail
}
\maketitle

@@

\subsection{Gradient boosted trees}
A gradient boosted trees $F_m(x)$ is updated as follow for a new tree $f_m$ built at iteration $m$ is

@@

\subsection{Customer Features}
All categorical data such as age group, gender, income group are handled as dummy variables. Address latitude and longitude are treated as continuous variables.

@@

 \item Similarly for $training_2, training_3, ... training_N$, the prediction for testing is the average of $N$ prediction of $testing$

@@

In practice, a diversified combination of stacking features from different algorithms (KNN, RandomForest, SVM, NN, etc.)
will usually outperform stacking using only one algorithm.
Since we only used xgboost here, we tried to compensate this by building several stacking features using randomized parameters.

Fig. 1 shows the AUC perfomance of CV result and 30\% of testing data. Although there's a difference of AUC between local CV and 30\% of testing data,
there is a strong correlation between CV and testing data. The AUC is higher when stacking is applied and result keep improving when we used more stacking features.

\begin{figure}[ht!]
\centering
\includegraphics[width=110mm]{Rplot.png}
\caption{AUC of 5folds CV result and 30\% testing data using different number of stacking features \label{overflow}}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Hyperparameters Optimization}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
We applied grid search on a subset of parameters. In general, $max\_depth$, $min\_child\_weight$, $gamma$, $lambda$ and $alpha$ are tuned for model complexity,
 $subsample$, $colsample\_bytree$ are tuned to avoid overfitting, $scale\_pos\_weight$ is used to re-balance dataset.
 In order to speed things up we used a high $eta$ (shrinkage) in the first stage and ranked parameter combinations based on cross validation score.
 For the parameter combinations with top 5\% ranking, we re-trained the model using a lower $eta$ and selected the one with best cross validation score.

@@

>>>>

\usepackage{booktabs}

@@

%If there are too many authors, use \authorrunning
%\authorrunning{First Author et al.}
\institute{
    Data Scientist, Cathay Pacific - Asia Miles
    \\ \authormail
}
\maketitle

@@

\subsection{Gradient boosted trees}
A gradient boosted trees $F_m(x)$ is updated as follows for a new tree $f_m$ built at iteration $m$ is

@@

\subsection{Customer Features}
All categorical data such as age group, gender, income group are one-hot-encoded. Address latitude and longitude are treated as continuous variables.

@@

 \item Similarly for $training_2, training_3, ... training_N$, the prediction for testing is the average of $N$ predictions of $testing$

@@

In practice, a diversified combination of stacking features from different algorithms (KNN, RandomForest, SVM, NN, etc.)
will outperform stacking using only one algorithm.
Since we only used XGboost here, we tried to compensate this by building several stacking features using randomized parameters to achieve diversification.

\textbf{Fig. 1} shows the AUC perfomance of Local 5-folds Cross Validation result and 30\% of testing data using same parameters and seed.
 Although there's a difference in AUC between local CV and 30\% of testing data,
 there is a strong correlation on AUC between CV and testing data. The AUC improved when stacking is applied and result keep improving
 when more randomized stacking features is used.

\begin{figure}[ht!]
\centering
\includegraphics[width=125mm]{Rplot.png}
\caption{AUC of CV result and 30\% testing data using different number of stacking features. One standard deviation of the CV score is plotted via error bar. \label{overflow}}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Hyperparameters Optimization}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
We applied grid search on a subset of parameters. In general, $max\_depth$, $min\_child\_weight$, $gamma$, $lambda$ and $alpha$ are tuned for model complexity,
 $subsample$, $colsample\_bytree$ are tuned to avoid overfitting, $scale\_pos\_weight$ is used to re-balance dataset.
 In order to speed things up we used a high $eta$ (shrinkage) in the beginning and ranked parameter combinations based on cross validation score.
 For the parameter combinations with top 5\% ranking, we re-trained the model using a lower $eta$ and selected the one with best cross validation score.

@@

Below are the parameters we used during training:

\begin{table}[h!]
  \centering
  \caption{Parameters Optimization for XGboost}
  \label{tab:table1}
  \begin{tabular}{p{3cm}p{3cm}p{4cm}p{2cm}}
    \toprule
    Parameters & Description & Range of values & Final Choice \\
    \midrule
    $eta$ & Shrinkage in update & [0.005, 0.01, 0.05, 0.1] & 0.005 \\
    $max\_depth$ & Maximum depth of tree & [3, 4, 5, 6, 7, 8] & 3 \\
    $colsample\_bytree$ & Subsample ratio of columns when constructing each tree & [0.8, 0.85, 0.9, 0.95, 1] & 0.9 \\
    $colsample\_bylevel$ & Subsample ratio of columns for each split, in each level & [0.8, 0.85, 0.9, 0.95, 1] & 1 \\
    $subsample$ & Subsample of data & [0.7, 0.8, 0.9, 1] & 1 \\
    $lambda$ & L2 regularization & [0.1, 0.5, 1, 5, 10, 20] & 5 \\
    $alpha$ & L1 regularization & [0, 0.1, 0.5, 1, 5, 10] & 0 \\
    \bottomrule
  \end{tabular}
\end{table}
